Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2020-05-12 reports/paper1/paper.tex
Paper

For each position $(x,y)$, a test statistic was calculated
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection. The variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{ma2012varaince, yang2010noise}. A gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} was used with an identity link. The fitting of the model was done using the held out replicated projections of the sample (see Section \ref{subsection:appratus}). These replicated projections were manually segmented so that only pixels which represent the test sample were used. This provided variance-mean data, where each pixel is a data point, which was used to fit the variance model. The variance was predicted using the grey value in the simulated projection as the predictor variable.

>>>>

For each position $(x,y)$, a test statistic was calculated
\begin{equation}
  Z_{x,y} =
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{{s}^2\left[\emph{aRTist}_{x,y}\right]}
  }
\end{equation}
where ${s}^2\left[\emph{aRTist}_{x,y}\right]$ is the predicted grey value variance of pixel $(x,y)$ in the projection using \emph{aRTist} as a predictor. The variance model ${s}^2\left[\emph{aRTist}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{ma2012varaince, yang2010noise}. A gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} was used with an identity link. The fitting of the model was done using the held out replicated projections of the sample (see Section \ref{subsection:appratus}). These replicated projections were manually segmented so that only pixels which represent the test sample were used. This provided variance-mean data, where each pixel is a data point, which was used to fit the variance model. The variance was predicted using the grey value in the simulated projection as the predictor variable.
